The \dealii{} Library, Version 9.2

### 2020-06-07 9.2/paper.tex
Resolve another TODO.
Minor typos fixed

        An example is that \texttt{DiscreteTime} ensures that the final time step ends

@@

        lengthening or shortening to final time step.

@@

\todo[inline]{Luca: Your section}

@@

Certain types of quantities in a simulation are constants fully known
at compile time. They can be pre-calculated and stored in the
compiled executable in order to avoid unnecessary initialization during
runtime. C++11 and later standards enables such computations by
marking variables and functions with the \texttt{constexpr} keyword.

>>>>

        For instance, \texttt{DiscreteTime} ensures that the final time step ends

@@

        lengthening or shortening the final time step.

@@

@@

Certain types of quantities in a simulation are constants fully known
at compile time. They can be pre-calculated and stored in the
compiled executable in order to avoid unnecessary initialization during
runtime. C++11 and later standards enable such computations by
marking variables and functions with the \texttt{constexpr} keyword.
